---
title: "Netflix Analysis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library("dplyr")
library("ggplot2")
library("ggrepel")
library("DT")
library("tidyr")
library("forcats")
df_netflix <- read.csv("finalMergedNetflixData.csv")
df_netflix <- as.data.frame(df_netflix)
```

Column {data-width=350}
-----------------------------------------------------------------------

### pie chart of movies and tv shows ~ arka
```{r}
ratio=table(as.matrix(df_netflix$type))
pie(ratio, main = "Movies and TV shows",col = rainbow(length(ratio)))
legend("topright", c("Movies","TV Shows"),
   fill = rainbow(length(ratio)))

```

### Table showing processed data ~ sourish

```{r}
datatable(df_netflix)
```

Column {data-width=500}
-----------------------------------------------------------------------
### stacked bar chart representation of shows and movies over the years ~ yash

```{r}

```


### Heatmap of month vs year releases ~ arka

```{r}

```

### regression chart of number of releases per year ~ arka

```{r}
a <- rle(sort(df_netflix$release_year))
plot(a$values,a$lengths,xlab="Release Year",ylab="No. of Releases")
k<-data.frame(a$lengths,a$values)
abline(lm(a$lengths~a$values,data=k),col='red') 


```

### bar chart of ratings of shows region wise ~ prakhar

### stacked bar chart of ratings and number of votes region wise ~ prakhar

### regression of rating vs release year ~ yash

### Number of shows available in Netflix as a function of time
```{r}
df_netflix$date_added <- as.Date(df_netflix$date_added, format = "%B %d, %Y")
df_netflix
df_by_date <- df_netflix %>% group_by(date_added,type) %>% summarise(addedToday = n()) %>% 
            ungroup() %>% group_by(type) %>% mutate(Total_Number_of_Shows = cumsum(addedToday), label = if_else(date_added == max(date_added,na.rm = T), as.character(type), NA_character_))


df_by_date  %>% 
                ggplot(aes(x = date_added, y = Total_Number_of_Shows, color = type)) + geom_line(size = 2) + 
                    theme_bw(base_size = 20) + 
                    scale_x_date(date_breaks = '2 years', date_labels = "%Y") + 
                    theme(legend.position = 'none') +
                    geom_text_repel(aes(label = label), size = 8,na.rm = TRUE, nudge_y = 100)

```

### Show Categories: Correlations and most frequent

``` {r}
df_show_categories <- df_netflix %>% 
                        select(c('show_id','type','listed_in')) %>% 
                        separate_rows(listed_in, sep = ',') %>%
                        rename(Show_Category = listed_in)
df_show_categories$Show_Category <- trimws(df_show_categories$Show_Category)
head(df_show_categories)
df_show_categories %>% mutate(Show_Category = fct_infreq(Show_Category)) %>% 
        ggplot(aes(x = Show_Category)) + 
            geom_bar() + scale_x_discrete() + facet_wrap(~type, scales = 'free_x') + coord_cartesian(xlim = c(1,20)) + theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5))
```

### Correlation of parental rating and avg rating ~ sourish
```{r}

gg <- ggplot()
gg <- gg + geom_point(data=df_netflix,
                      aes(x=rating, y=averageRating, color=type))
gg <- gg + labs(x="parental rating", y="average rating", title=NULL)
gg <- gg + theme_bw()
gg
```

### correlation of duration and avg rating ~ yash